---
title: "{article_title}"
description: >
  {article_summary}
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Article title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<!--
Template notes
- This is intended to be used as a website-only article (fast iteration while the API evolves).
- Create via `usethis::use_article("name")` to ensure it is added to .Rbuildignore automatically.
- Keep this guide task-oriented. Link to Reference pages for function details.
-->

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  message = FALSE,
  warning = FALSE
)
```

## Goal

State the concrete goal of this article:

- By the end, you will be able to {goal_action} with {pkg}.

## Audience

Who is this for?

- Primary audience: {audience_primary}
- Secondary audience: {audience_secondary}

## Prerequisites

What the user needs before starting:

- R version: >= {r_version_min}
- Packages: `{pkg}`, `{dependency1}`, `{dependency2}`
- Data requirements: {data_requirements}

Optionally provide a small checklist:

- [ ] {requirement_1}
- [ ] {requirement_2}
- [ ] {requirement_3}

## Setup

```{r}
library({pkg})
```

If you need optional dependencies:

```{r}
# install.packages("{optional_pkg}")
# library({optional_pkg})
```

## Overview of the workflow

Describe the workflow in 3 to 6 steps. Example:

1. Prepare inputs
2. Fit the model
3. Inspect fit
4. Extract outputs
5. Visualize or report

## Step 1: Prepare inputs

Explain the expected structure and then provide minimal code.

```{r}
# x <- {pkg}::example_data()
# x <- {pkg}::prep_data(x, ...)
```

### Checks

Include lightweight checks to reduce user frustration:

```{r}
# stopifnot(is.data.frame(x))
# {pkg}::validate_inputs(x)
```

## Step 2: Run the main procedure

```{r}
# res <- {pkg}::do_the_thing(x, ...)
```

Explain key arguments briefly and link to Reference pages for full details.

## Step 3: Inspect results

```{r}
# summary(res)
# plot(res)
```

If you provide printed output, keep it short and stable.

## Step 4: Extract what you need

```{r}
# out <- {pkg}::extract_results(res)
# out
```

If appropriate, include a table-friendly object.

## Pitfalls

List common pitfalls and quick fixes.

## Variations (optional)

Describe optional paths and trade-offs.

## See also

- Reference: {reference_link}
- Articles index: {articles_index_link}