---
title: "Get started with REPO"
description: >
  A guided, minimal happy-path workflow for REPO. This page is intentionally short.
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Get started with REPO}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<!--
Template notes
- To make this appear as the top-level "Get started" link in pkgdown, name the file after your package:
  - Example: vignettes/<package>.Rmd
  - If the package name contains a dot (example: pack.down), use a dash in the vignette name (example: pack-down.Rmd).
- Keep this guide short and stable. Move advanced details to other articles.
-->

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  message = FALSE,
  warning = FALSE
)
```

## What you will do

In this guide, you will:

1. Install REPO
2. Run one minimal, stable example
3. Learn where to go next (Workflows, Reference, FAQ)

## Install

```{r}
# Recommended (fast)
# install.packages("pak")
pak::pak("ORG/REPO")
```

Alternative:

```{r}
# install.packages("remotes")
remotes::install_github("ORG/REPO")
```

## Load the package

```{r}
library(REPO)
```

## A minimal workflow

This section should demonstrate a single, stable happy path.

### Inputs

Briefly describe the expected inputs:

- Data format: {data description}
- Required columns: {columns}
- Assumptions: {assumptions}

### Step 1. Prepare data

```{r}
# Replace with a real helper once stable
# data <- REPO::example_data()
# data <- REPO::prep_data(data, ...)
```

### Step 2. Fit the model

```{r}
# fit <- REPO::fit_model(data, ...)
```

### Step 3. Inspect results

```{r}
# summary(fit)
# plot(fit)
```

### Step 4. Extract key outputs

```{r}
# out <- REPO::extract_results(fit)
# out
```

## Common pitfalls

- **Pitfall 1**: {short description}
  - Fix: {short fix}

- **Pitfall 2**: {short description}
  - Fix: {short fix}

## Where to go next

- **Workflows**: See the Articles section for end-to-end guides by module.
- **Reference**: Use Reference pages to understand individual functions and arguments.
- **FAQ**: See the FAQ and troubleshooting article for common issues.

## Session info

If you report issues, include your session info:

```{r}
sessionInfo()
```